\documentclass[12pt,ebook,oneside]{book}

\usepackage{graphicx} 
\usepackage{layouts} 
\usepackage{hyperref} 
\textheight=1.2\textheight

\begin{document}

\section{How to use the converter}

\begin{itemize}
\item Download the zip file: \url{https://github.com/kingofmen/CK2toEU4/archive/master.zip}.
\item Unpack it. 
\item Ignore the source code unless you intend to modify it. 
\item Copy the CK2 savegame you intend to convert into the release
  directory. NB! The save must not be compressed!
\item Start the CK2toEU4 executable. 
\item Go to File->Load file and select your savegame. 
\item Wait for it to load - it will take a minute or two. If it takes
  more than five minutes, you have either a very slow computer, or a
  problem - go to Troubleshooting, below. 
\item Go to Actions->Convert to EU4. Wait until it says ``Done
  writing''. If the output stops for more than a few minutes with any
  other message, especially one starting `Error', go to
  Troubleshooting. 
\item Conversion is now done. Go to the Output directory. It should
  contain `converted.eu4'. Move this to your EU4 savegames folder; on
  my machine this is on C:\\Users\\UserName\\My Documents\\Paradox
  Interactive\\Europa Universalis IV, but installations differ. 
\item Start EU4 as usual. The converted game should appear as a
  regular saved game; select your country and play. If it crashes or
  hangs on loading, or within a few days of starting, go to
  Troubleshooting. 
\item Conquer \emph{All} the Pixels! 
\end{itemize}

\section{Mods and DLCs}

The converter has not been tested with all possible combinations of
DLCs. It is intended to work with fully-updated CK2 and EU4 games;
that is, your CK2 savegame should be from a game with Charlemagne,
Legacy of Rome, Rajas of India, Sons of Abraham, Sunset Invasion, The
Old Gods, The Republic, and Sword of Islam. It \emph{may or may not}
work if you're missing any of these. If it does not, send me the save
as described in the section on troubleshooting, below, and if it's an
\emph{easy} fix I'll fix it. If it's a lot of work I won't.

Similarly, the target EU4 install has Art of War, Common Sense,
Conquest of Paradise, El Dorado, Res Publica, The Cossacks, and Wealth
of Nations. If you're missing one or more, the converter \emph{may or
  may not} work. However, it certainly will \emph{not} work unless you
provide your own input save from your EU4 install. To do this, start a
fresh game in 1444. Save on the first day, calling the save `input';
do \emph{not} compress. Copy this new save to the release\\maps
directory in your converter install.

Finally, mods: The converter \emph{may or may not} work with modded
savegames. Generally, map mods are going to be a problem, though you
can try to supply your own province mapping by editing
release\\maps\\provinces.txt. If you want to target an EU4 mod, you
should probably provide an input save from that mod, as described
above.

\section{Troubleshooting}

This is not my day job, but in my copious free time I do try to
support my converters. If you have a problem, first go through this
checklist:

\begin{itemize}
\item Is your CK2 savegame compressed? If so, unzip it.
\item Is your converted save invisible in EU4? Two things:
\begin{itemize}
\item Did you move it to your EU4 savegame folder?
\item Did you click ``Show incompatible saves''? I've had many
  ``incompatible'' converted savegames work perfectly well.
\end{itemize}
\item Targeting a mod or a non-complete DLC collection? Did you
  provide your own input save?
\end{itemize}

Upload your (zipped) Crusader Kings
savegame and the converter logfile somewhere, then send me (``King of Men'') a PM on Paradox,
Ederon, or (``King\_of\_Men'') reddit with a link to the upload. In
your PM, say which steps of the checklist above you went through. This
will assure me that you read the documentation. If your PM is missing the
logfile or checklist, or the save is uncompressed or not present, will give
me the strong impression that you didn't do much to help yourself
before asking me. This will have a bad effect on my eagerness to help
you out.

Try to be as specific as possible about what the problem is - I cannot debug
``things look weird''. Screenshots and province IDs are often
helpful. I'll run the debugging version of the converter and try to fix the
problem. If you are skilled at C++ development in Windows you can also
try to compile in debug mode and run gdb on it. 

\section{Encouragement}

If you'd like to encourage me to work on this sort of thing in the
future, you can:
\begin{itemize}
\item Send me a PM saying ``Hey, your converter is great!'' 
\item Comment on my AARs, either at Ederon, at the Paradox forums, on
  my blog ynglingasaga.wordpress.com, or on reddit.
\item Donate! The aforementioned blog, and my converter site
  sites.google.com/site/komskustomkonverters, both have donation
  buttons.
\end{itemize}

\end{document}
